---
title: "WWE Extreme Attribution"
output:
  html_document:
    df_print: kable
    toc: true
    toc_float: true
    toc_collapsed: true
toc_depth: 1
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Goal of Analysis


```{r startup, echo=F, results = 'hide', message=F, cache=F}
library(DBI)
library(odbc)
library(tidyverse)
library(dbplyr)
library(lubridate)
library(CausalImpact)


# source query and get dataframe
con <- dbConnect(odbc(), "Athena")
source("query.R")
world <- dbGetQuery(con, world_query)
rpi_7d <- dbGetQuery(con, revenue_7day)
```


```{r preprocessing, echo=F, eval=T}

# world
pdata_world <- world %>% 
  mutate(date = ymd(date)) %>% 
  mutate_at(vars(all_installs:dau), as.numeric) %>% 
  dplyr::select(organic_installs, everything()) %>% 
  replace(is.na(.), 0)

dates_world <- pdata_world$date

# installs as target
# pdata_world_covariates_ts <- zoo(pdata_world %>% dplyr::select(organic_installs, daily_spend), dates_world)
pdata_world_ts <- zoo(pdata_world %>% dplyr::select(organic_installs), dates_world)

# revenue as target
# pdata_world_rev_covariates_ts <- zoo(pdata_world %>% dplyr::select(organic_revenue, daily_spend), dates_world)
pdata_world_rev_ts <- zoo(pdata_world %>% dplyr::select(organic_revenue), dates_world)

# DAU as target
pdata_world_dau_ts <- zoo(pdata_world %>% dplyr::select(dau), dates_world)


# evergreen vars
pre.period <- as.Date(c("2019-06-13", "2019-06-23"))
post.period <- as.Date(c("2019-06-24", "2019-07-15"))
aug.pre.period <- as.Date(c("2019-07-28", "2019-08-04"))
aug.post.period <- as.Date(c("2019-08-05", "2019-08-14"))

# for ggplot extreme and other key events
extreme_begin <- as.Date('2019-06-24')
extreme_end <- as.Date('2019-07-14')
extreme_overlay <- data.frame(start = extreme_begin, end = extreme_end)

#aug tv
aug_tv_begin <- as.Date('2019-08-05')
aug_tv_end <- as.Date('2019-08-14')
aug_tv_overlay <- data.frame(start = aug_tv_begin, end = aug_tv_end)

WWE_usa_launch <- as.Date('2019-05-28')
WWE_usa_launch_end <- as.Date('2019-05-30')
usa_launch_overlay <- data.frame(start = WWE_usa_launch, end = WWE_usa_launch_end)
```

# Summary and Contextual Overview {.tabset .tabset-fade .tabset-pills}


## Organic Installs
```{r overview_installs, echo=FALSE, message=FALSE, warning=FALSE}

# Organic Install Trend
pdata_world %>% dplyr::select(date, organic_installs) %>% 
  ggplot(aes(x = date, y = organic_installs)) +
  geom_line() +
  geom_rect(data = extreme_overlay, inherit.aes = F,
            aes(xmin = start, xmax = end,
                ymin = -Inf, ymax = Inf,
                fill = "Extreme Rules"),
            alpha = 0.1) +
  geom_rect(data = usa_launch_overlay, inherit.aes = F,
            aes(xmin = start, xmax = end,
                ymin = -Inf, ymax = Inf,
                fill = "USA Launch"),
            alpha = 0.1) +
  geom_rect(data = aug_tv_overlay, inherit.aes = F,
            aes(xmin = start, xmax = end,
                ymin = -Inf, ymax = Inf,
                fill = "August TV & Arena"),
            alpha = 0.1) +
    scale_fill_manual(name = element_blank(), 
                      values = c("Extreme Rules" = "black", 
                                 "USA Launch" = "blue", 
                                 "August TV & Arena" = "green"))
```


## Organic Revenue
```{r overview_revenue, echo=FALSE}

# Organic Revenue Trend
pdata_world %>% dplyr::select(date, organic_revenue) %>% 
  ggplot(aes(x = date, y = organic_revenue)) +
  geom_line() +
  geom_rect(data = extreme_overlay, inherit.aes = F,
            aes(xmin = start, xmax = end,
                ymin = -Inf, ymax = Inf,
                fill = "Extreme Rules"),
            alpha = 0.1) +
  geom_rect(data = usa_launch_overlay, inherit.aes = F,
            aes(xmin = start, xmax = end,
                ymin = -Inf, ymax = Inf,
                fill = "USA Launch"),
            alpha = 0.1) +
  geom_rect(data = aug_tv_overlay, inherit.aes = F,
            aes(xmin = start, xmax = end,
                ymin = -Inf, ymax = Inf,
                fill = "August TV & Arena"),
            alpha = 0.1) +
    scale_fill_manual(name = element_blank(), 
                      values = c("Extreme Rules" = "black", 
                                 "USA Launch" = "blue", 
                                 "August TV & Arena" = "green"))
```

## DAU (All)
```{r overview_dau, echo=FALSE}

# Organic Revenue Trend
pdata_world %>% dplyr::select(date, dau) %>% 
  ggplot(aes(x = date, y = dau)) +
  geom_line() +
  scale_y_continuous(labels = scales::comma) +
  geom_rect(data = extreme_overlay, inherit.aes = F,
            aes(xmin = start, xmax = end,
                ymin = -Inf, ymax = Inf,
                fill = "Extreme Rules"),
            alpha = 0.1) +
  geom_rect(data = usa_launch_overlay, inherit.aes = F,
            aes(xmin = start, xmax = end,
                ymin = -Inf, ymax = Inf,
                fill = "USA Launch"),
            alpha = 0.1) +
  geom_rect(data = aug_tv_overlay, inherit.aes = F,
            aes(xmin = start, xmax = end,
                ymin = -Inf, ymax = Inf,
                fill = "August TV & Arena"),
            alpha = 0.1) +
    scale_fill_manual(name = element_blank(), 
                      values = c("Extreme Rules" = "black", 
                                 "USA Launch" = "blue", 
                                 "August TV & Arena" = "green"))
```

# Attribution Modelling {.tabset .tabset-fade .tabset-pills}


## Organic Installs
```{r CasualImpact_TS_Only, echo=F}
impact_world_ts_only <- CausalImpact(pdata_world_ts, pre.period, post.period)
plot(impact_world_ts_only)
summary(impact_world_ts_only)
# summary(impact_world_ts_only, "report")
```

## Organic Revenue
```{r CasualImpact_revenue, echo=F}
revenue_impact_world_ts_only <- CausalImpact(pdata_world_rev_ts, pre.period, post.period)
plot(revenue_impact_world_ts_only)
summary(revenue_impact_world_ts_only)
# summary(revenue_impact_world_ts_only, "report")
```

## DAU
```{r CasualImpact_dau, echo=F}
dau_impact_world_ts_only <- CausalImpact(pdata_world_dau_ts, pre.period, post.period)
plot(dau_impact_world_ts_only)
summary(dau_impact_world_ts_only)
```


# Cost Per Install

CPI for paid installs does decrease for the Extreme Rules time period overall. The trend chart shows this visibly starting to decline when Extreme Rules begins.
```{r cpi, echo=F, warning=FALSE}
# Overall CPI
pdata_world %>% mutate(period = if_else(date >= '2019-06-13' & date <= '2019-06-24', "pre_period",
                                        if_else(date >= '2019-06-25' & date <= '2019-07-14', "post_period", "other"))) %>% 
  group_by(period) %>% 
  filter(period != "other") %>% 
  summarise(TotalSpend = sum(daily_spend),
            TotalPaidInstalls = sum(paid_installs)) %>% 
  mutate(CPI = scales::dollar(TotalSpend / TotalPaidInstalls),
         TotalSpend = scales::dollar(TotalSpend))


# CPI daily trend
pdata_world %>% mutate(CPI = daily_spend / paid_installs) %>% 
  ggplot(aes(x = date, y = CPI)) +
  geom_line() +
  scale_y_continuous(labels = scales::dollar) +
  geom_rect(data = extreme_overlay, inherit.aes = F,
          aes(xmin = start, xmax = end,
              ymin = -Inf, ymax = Inf,
              fill = "Extreme Rules"),
          alpha = 0.1) +
  geom_rect(data = usa_launch_overlay, inherit.aes = F,
          aes(xmin = start, xmax = end,
              ymin = -Inf, ymax = Inf,
              fill = "USA Launch"),
          alpha = 0.1) +
  scale_fill_manual(name = element_blank(), values = c("Extreme Rules" = "black", "USA Launch" = "blue"))
```


```{r organic_ltv, echo=F}
# cbind onto query of 7day ltv
rpi_7d %>% mutate(attributed_organic_installs = impact_world_ts_only$summary$AbsEffect[2],
                  estimated_RPI_365_ltv_3x_multiplier = rpi_7day * 3) %>% 
  mutate(estimated_total_organic_revenue = estimated_RPI_365_ltv_3x_multiplier * attributed_organic_installs) %>% 
  mutate(revenue_7_day = scales::dollar(revenue_7_day),
         rpi_7day = scales::dollar(rpi_7day),
         estimated_RPI_365_ltv_3x_multiplier = scales::dollar(estimated_RPI_365_ltv_3x_multiplier),
         estimated_total_organic_revenue = estimated_total_organic_revenue) %>%
  mutate(estimated_total_organic_revenue_plus_ads_revenu =scales::dollar(1.34 * estimated_total_organic_revenue)) %>% t()
```

